The Noisy Work of Uncertainty Visualisation Research: A Review

### 2024-10-10 paper.qmd
updated general comments

<!-- TODO 
- convert to American spelling 
  (Susan) Is this necessary? I'm not sure it matters as long as you're consistent...
- May not need to reference the same paper again and again
  - I am not sure when I need a citation and when I dont. Sometimes I could literally cite hundreds of papers to make a point, so I'm not sure if i should cite any at all.
- examples that aren't maps? Sure are a lot of maps.
-->

>>>>

<!-- TODO 
- (Di) convert to American spelling 
  (Susan) Is this necessary? I'm not sure it matters as long as you're consistent...
- (Susan) examples that aren't maps? Sure are a lot of maps.
-->
